---
title: "MyPlotly Graph"
author: "Tushar"
date: "April 10, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Understanding Gas Mileage
- Using the mtcars dataset we plot can attempt to understand the relationship of various factors to gas mileage (mpg).

- We plot weight (wt) vs. mileage (mpg) spatially along the x/y axes. 
- We visualize the number of cylinders (cyl) as colors and the amount of horsepower (hp) as the size of an individual point in the plot.

## Slide with R Code
`suppressPackageStartupMessages(library(plotly))
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp,
        text = ~paste("Weight: ", wt, '<br>MPG:', mpg),
        type = "scatter", mode = "markers") %>%
  layout(title = "Car Data")`



## Slide with Plot

```{r cars}
suppressPackageStartupMessages(library(plotly))
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), size = ~hp,
        text = ~paste("Weight: ", wt, '<br>MPG:', mpg),
        type = "scatter", mode = "markers") %>%
  layout(title = "Car Data")
  
```





